---
title: "Gen Z Dating Dynamics"
subtitle: "Statistical Insights and Neuroscience Perspectives on the 'Undateable Generation"
author: 
  - Chay Park
thanks: "Code and data are available at: https://github.com/Chay-HyunminPark/Undateable-generation."
date: today
date-format: long
abstract: "Describe more about why it matters"
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```


# Introduction

broader context to motivate

### below is more related to commitment issue

According to Pew Research, Generation Z, also abbreviated for Gen Z, is defined as a generation born betweeen 1997 to 2012 (Dimock, 2019). 
Young people aren't dating and having sex the same way past generations have. Just 1 in 10 are "committed to being committed," (Klein, 2022). There are many possible reasons addressed, gen z is entering adulthood during a particulary tenuous time, the Covid-19 pandemic, ever-worsening climate change, and financial stability. Many feel they need to be stable for themselves before picturing themselves with another person. Perhaps this is supporting why Gen Z is described as a hyper-focused generation. 
Stephanie Coontz, the director of research and public education for the US-based Council on Contemporary Families once said "back in the 1960s and 70s, your average 25-year-old man could support a family with his income and not expect his wife to work," and Klein pointed out it no longer fits contemporary circumstances. On the other hand, Gen Z is prioritising a solid financial foundation as individuals, which is lengthening the path toward marriage. Gen Z desire to gain "financial independence" before they settle down with a long-tern partner (Klein, 2022).

New dating terms such as "talking to someone", "hanging out", "situationships" are developed. Putting everything else but actual commitment. Now the dating is described as 'casual', 'easy-going' at a 'surface level'.

Dating in the digital age adds an additional layer of complexity. 
"Everyone's scared to commit because they're worried that someone better is out tere."
Dating apps can foster an environment where inappropriate behaviour thrives, like treating people as throwaways. 



Endless options every time they open a dating app. Commiting to someone means that you're cutting yourself from all those other options.

In this paper, I will demonstrate in neuroscience perspective 



- Way to understand how different formative experiences interact with the life-cycle and aging process to shape people's views of the world. 
 
Gen Z dating issue was raised ~ 




"The estimand is the difference in whether an applicant would be called back if their CV signalled White with a felony vs Black without. This is considered in terms of applications to jobs in Milwaukee."
"The estimand is the difference in whether a mother would be employed if she had three children compared with if she had two children. This is considered in terms of those who would have a third birth only if the first two children were of the same sex."




# Data {#sec-data}

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up


### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.


# Results



# Discussion

## First discussion point {#sec-first-point}
### Lack of testosterone
- increase in obesity
- less physical society

## Second discussion point

### The rise of dating apps has changed not just how people get dates, but how they behave in real life.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows... 

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

```{r}
#write_parquet(x = nationscape_data,
              #sink = "nationscape_data_cleaned.parquet")
```

\newpage


# References


